\chapter*{Acknowledgments}
With deep gratitude I thank my advisors Bennett Goldberg and Anna Swan for crafting me into the physicist I am today.
Special thanks to Bennett for giving me the freedom to follow my ideas, and to Anna for having the patience to listen to my latest experimental foible.

Many thanks to my many collaborators.
Specifically I would like to thank the reputable graphene strain theorists Harold Park, Zenan Qi and Vitor Pereira, the brilliant Kekul\'e theorists Claudio Chamon and Tom Iadecola, the masters of helium scattering Michael El-Batanouny and Colin Howard, and the graphene growth gurus at UT Austin Rod Ruoff, Richard Piner, and Ji Won Suk.
Additional thanks go to my lab mates Sebastian Remi, Xuanye Wang, and Jason Christopher and my cohort at BU, especially Alan Gabel, Elsa Abreu, John Ogren, Cory Fantasia, and Kang Liu.

Thanks to the folks at SIF, principally Heitor Mourato, Bob Fazio, and Joe Volho, who routinely made substance out of my imagination.
Special thanks to the late Bob Kingsland, a great teacher who was always able to make me feel at home and at ease-onwards and upwards.

I would like to thank my parents and most loyal fans, Anne Mercier and Greg Kitt, for giving me the traits which carried me through graduate school: An expectation of myself and the confidence to work with my hands.
I would also like to thank my wife's parents, Dede and Stan Colwell, for their acceptance and encouragement.

Most importantly I would like to thank my wife, Jess, for helping me get through my N+1 failures.
I could never have done this without her unwavering love and support.

\newpage